### 2015-04-15 Kokkos_PG_Compilation.tex
Updated style of the Guide . This comments out the SAND Report style
The stuff is still in if we really need to its not that hard to go back.

Kokkos consists mainly of header files. 
Only a few functions have to be compiled into object files outside of the application's source code.
Those functions are contained in \verb!.cpp! files inside the \lstinline|kokkos/core/src| directory and its subdirectories.
The files are internally protected with macros to prevent compilation if the related execution space is not enabled. 
Thus, it is not necessary to create a list of included object files specific to your compilation target.
One may simply compile all \verb!.cpp! files. 
The enabled features are controlled via macros which have to be provided in the compilation line or in the \lstinline|KokkosCore_config.h| include file. 
A list of macros can be found in Table \ref{TBL:CompileMacros}.
\begin{table}
\caption{Table of configuration Macros}
\label{TBL:CompileMacros}
\begin{small}
\begin{tabular}[t]{p{0.25\textwidth}p{0.3\textwidth}p{0.42\textwidth}}
\hline\hline
Macro & Effect & Comment \\
\hline
{\tiny KOKKOS\_HAVE\_CUDA} & Enable the CUDA execution space. & Requires a compiler capable of understanding CUDA-C. See Section \ref{S:build:CUDA}. \\
{\tiny KOKKOS\_HAVE\_OPENMP} & Enable the OpenMP execution space. & Requires the compiler to support OpenMP (e.g., \verb!-fopenmp!). \\
{\tiny KOKKOS\_HAVE\_PTHREADS} & Enable the Threads execution space. & Requires linking with libpthread.\\
{\tiny KOKKOS\_HAVE\_Serial} & Enable the Serial execution space. & \\
{\tiny KOKKOS\_HAVE\_CXX11} & Enable internal usage of C++11 features. & The code needs to be compile with the C++11 standard. Most compilers accept the \verb!-std=c++11! flag for this.\\
{\tiny KOKKOS\_HAVE\_HWLOC} & Enable thread and memory pinning via hwloc. & Requires linking with libhwloc.\\
\hline\hline
\end{tabular}
\end{small}
\end{table}

@@

\hline
   HWLOC\_PATH (IN): & Path to the hardware locality library. \\

@@

@@

Any Kokkos application compiled for CUDA embeds CUDA code via template metaprogramming.
Thus, the whole application must be built with a CUDA-capable compiler.
(At the moment, the only such compiler is NVIDIA's NVCC.)
More precisely, every compilation unit containing a Kokkos kernel or a function called from a Kokkos kernel has to be compiled with a CUDA-capable compiler. 
This includes files containing \lstinline|Kokkos::View| allocations, which call an initialization kernel.

>>>>

Kokkos consists mainly of header files. 
Only a few functions have to be compiled into object files outside of the application's source code.
Those functions are contained in \verb!.cpp! files inside the \lstinline|kokkos/core/src| directory and its subdirectories.
The files are internally protected with macros to prevent compilation if the related execution space is not enabled. 
Thus, it is not necessary to create a list of included object files specific to your compilation target.
One may simply compile all \verb!.cpp! files. 
The enabled features are controlled via macros which have to be provided in the compilation line or in the \lstinline|KokkosCore_config.h| include file. 
A list of macros can be found in Table \ref{TBL:CompileMacros}.
\begin{table}
\caption{Table of configuration Macros}
\label{TBL:CompileMacros}
\begin{small}
\begin{tabular}[t]{p{0.18\textwidth}p{0.3\textwidth}p{0.42\textwidth}}
\hline\hline
Macro & Effect & Comment \\
\hline
{\tiny KOKKOS\_HAVE\_CUDA} & Enable the CUDA execution space. & Requires a compiler capable of understanding CUDA-C. See Section \ref{S:build:CUDA}. \\
{\tiny KOKKOS\_HAVE\_OPENMP} & Enable the OpenMP execution space. & Requires the compiler to support OpenMP (e.g., \verb!-fopenmp!). \\
{\tiny KOKKOS\_HAVE\_PTHREADS} & Enable the Threads execution space. & Requires linking with libpthread.\\
{\tiny KOKKOS\_HAVE\_Serial} & Enable the Serial execution space. & \\
{\tiny KOKKOS\_HAVE\_CXX11} & Enable internal usage of C++11 features. & The code needs to be compile with the C++11 standard. Most compilers accept the \verb!-std=c++11! flag for this.\\
{\tiny KOKKOS\_HAVE\_HWLOC} & Enable thread and memory pinning via hwloc. & Requires linking with libhwloc.\\
\hline\hline
\end{tabular}
\end{small}
\end{table}

@@

@@

\hline
   KOKKOS\_USE\_TPLS (IN): & Enable optional third party libraries. \\
      \hspace{0.5cm}Options: & hwloc,librt \\
      \hspace{0.5cm}Default: & \\

\hline
   HWLOC\_PATH (IN): & Path to the hardware locality library if enabled. \\

@@

Any Kokkos application compiled for CUDA embeds CUDA code via template meta-programming.
Thus, the whole application must be built with a CUDA-capable compiler.
(At the moment, the only such compiler is NVIDIA's NVCC.)
More precisely, every compilation unit containing a Kokkos kernel or a function called from a Kokkos kernel has to be compiled with a CUDA-capable compiler. 
This includes files containing \lstinline|Kokkos::View| allocations, which call an initialization kernel.

### 2015-04-15 Kokkos_PG_LegacyCodeIntegration.tex
Updated style of the Guide . This comments out the SAND Report style
The stuff is still in if we really need to its not that hard to go back.

\section{Interoperability and Legacy Codes}

@@

\subsection{OpenMP, Pthreads and CUDA interoperability}

@@

\subsubsection{Cuda interoperabiltiy}

The most important thing to know for Cuda interoperability is that the
\lstinline|KOKKOS_INLINE_FUNCTION| macro evaluates to 
\lstinline|__host__ __device__ inline|. This means that calling a pure
\lstinline|__device__| function (for example Cuda intrinsics or device 
functions of libraries) must be protected with the \lstinline|__CUDA_ARCH__|
pragma.

@@

\subsubsection{OpenMP}

@@

\subsection{Legacy data structures}

@@

\subsection{Raw allocations through Kokkos}

@@

// Allocate an array of 150 int* in the Cuda UVM memory space
// This allocation is accessible from the host
int** 2d_array = (int**) kokkos_malloc<CudaUVMSpace>(150*sizeof(int*));

// Fill the pointer array with pointers to data in the Cuda Space
// Since it is not the UVM space you can access 2d_array[i][j] only inside a Cuda Kernel
for(int i=0;i<150;i++)
  2d_array[i] = (int*) kokkos_malloc<CudaSpace>(200*sizeof(int));
\end{lstlisting}

@@

\subsubsection{External memory management}

@@

  // Get the member_type of the team policy
  typedef TeamPolicy<host_space>::member_type t_team;
  // Run a 2D copy kernel using a TeamPolicy
  parallel_for(TeamPolicy<host_space>(n,m),KOKKOS_LAMBDA (const t_team& t) {
    const int i = t.team_rank();
    parallel_for(TeamThreadRange(t,m), [&] (const int& j) {
      h_b(i,j) = b[i][j];
    });
  });
  // Copy the data from the host to the device
  deep_copy(d_b,h_b);
}
\end{lstlisting}

@@

 \begin{lstlisting}
void MyKokkosFunction(double* a, const double* b, int n, int m) {
  // Define the host execution space and the view types
  typedef View<double*,DefaultHostExecutionSpace, Unmanaged> t_1d_view;
  typedef View<double**[3],LayoutRight, DefaultHostExecutionSpace, Unmanaged> 
     t_3d_view;

@@

  // Create a 3D view of the second external allocation
  // This assumes that the data had a row major layout (i.e. the third index is stride 1)
  t_3d_view d_b(b,n,m);
}
\end{lstlisting}

\subsubsection{Views as the fundamental data owning structure}

@@

\subsubsection{std::vector}

@@

Kokkos provides a drop in replacement for |std::vector| in the form of \lstinline|Kokkos::vector|.
Outside of parallel kernels its semantics are mostly the same as that of \lstinline|std::vector|, for
example assignments performs deep copies and resize and push functionality are provided.
One important difference is that it is valid to assign values to the elements of a const vector.

@@

@@

\subsection{Keeping track of data transfers}

>>>>

\chapter{Interoperability and Legacy Codes}

@@

\section{OpenMP, Pthreads and CUDA interoperability}

@@

\subsection{Cuda interoperabiltiy}

The most important thing to know for Cuda interoperability is that the provided macro
\lstinline|KOKKOS_INLINE_FUNCTION| evaluates to 
\lstinline|__host__ __device__ inline|. This means that calling a pure
\lstinline|__device__| function (for example Cuda intrinsics or device 
functions of libraries) must be protected with the \lstinline|__CUDA_ARCH__|
pragma.

@@

\subsection{OpenMP}

@@

\section{Legacy data structures}

@@

\section{Raw allocations through Kokkos}

@@

// Allocate an array of 150 int* in the Cuda UVM memory space
// This allocation is accessible from the host
int** 2d_array = (int**) kokkos_malloc<CudaUVMSpace>
                         (150*sizeof(int*));

// Fill the pointer array with pointers to data in the Cuda Space
// Since it is not the UVM space you can access 2d_array[i][j] 
// only inside a Cuda Kernel
for(int i=0;i<150;i++)
  2d_array[i] = (int*) kokkos_malloc<CudaSpace>(200*sizeof(int));
\end{lstlisting}

@@

\subsection{External memory management}

@@

  // Get the member_type of the team policy
  typedef TeamPolicy<host_space>::member_type t_team;
  // Run a 2D copy kernel using a TeamPolicy
  parallel_for(TeamPolicy<host_space>(n,m),
    KOKKOS_LAMBDA (const t_team& t) {
    const int i = t.team_rank();
    parallel_for(TeamThreadRange(t,m), [&] (const int& j) {
      h_b(i,j) = b[i][j];
    });
  });
  // Copy the data from the host to the device
  deep_copy(d_b,h_b);
}
\end{lstlisting}

@@

 \begin{lstlisting}
void MyKokkosFunction(int* a, const double* b, int n, int m) {
  // Define the host execution space and the view types
  typedef View<int*, DefaultHostExecutionSpace, Unmanaged> t_1d_view;
  typedef View<double**[3],LayoutRight, DefaultHostExecutionSpace, 
               Unmanaged> t_3d_view;

@@

  // Create a 3D view of the second external allocation
  // This assumes that the data had a row major layout 
  // (i.e. the third index is stride 1)
  t_3d_view d_b(b,n,m);
}
\end{lstlisting}

\subsection{Views as the fundamental data owning structure}

@@

\subsection{std::vector}

@@

Kokkos provides a drop in replacement for \lstinline|std::vector| with \lstinline|Kokkos::vector|.
Outside of parallel kernels its semantics are mostly the same as that of \lstinline|std::vector|, for
example assignments performs deep copies and resize and push functionality are provided.
One important difference is that it is valid to assign values to the elements of a const vector.

@@

\begin{lstlisting}
// Create a vector of 1000 double elements
Kokkos::vector<double> v(1000);
// Create another vector as a copy of v; 
// This allocates another 1000 doubles
Kokkos::vector<double> x = v;

parallel_for(1000, KOKKOS_LAMBDA (const int& i) {
   // Create a view of x; m and x will reference the same data.
   Kokkos::vector<double> m = x; 
   x[i] = 2*i+1;
   v[i] = m[i] - 1;
});

// Now x contains the first 1000 uneven numbers
// v contains the first 1000 even numbers
\end{lstlisting}

@@

There are no restrictions on calling non-Kokkos libraries outside of parallel kernels. 
However due to the polymorphic layouts of Kokkos views it is often required to test
layouts for compatibility with third party libraries. The usual Blas interface for example,
expects matrixes to be laid out in column major format (i.e. LayoutLeft in Kokkos). 
Furthermore it is necessary to test that the library can access the memory space 
of the view.

\begin{lstlisting}
template<class Scalar, class Device>
Scalar dot(View<const Scalar* , Device> a, 
           View<const Scalar*, Device> b) {
// Check for Cuda memory and call cublas if true
#ifdef KOKKOS_HAVE_CUDA
  if(Impl::is_same<typename Device::memory_space,
                            CudaSpace>::value ||
     Impl::is_same<typename Device::memory_space,
                            CudaUVMSpace>::value) {
    return call_cublas_dot(a.ptr_on_device(), b.ptr_on_device(),
                           a.dimension_0() );
  }
#endif

// Call CBlas on the host otherwise
  if(Impl::is_same<typename Device::memory_space,HostSpace>::value) {
    return call_cblas_dot(a.ptr_on_device(), b.ptr_on_device(),
                          a.dimension_0() );
  }
}
\end{lstlisting}

Note the \lstinline|Impl::is_same| construct can be replaced

### 2015-04-15 Kokkos_PG_MachineModel.tex
Updated style of the Guide . This comments out the SAND Report style
The stuff is still in if we really need to its not that hard to go back.

\subsection{Kokkos Execution Spaces}

@@

\subsubsection{Execution Space Instances}

@@

\subsubsection{Instances of Kokkos Memory Spaces}

@@

\section{Thread teams}\label{S:Model:Teams}

Kokkos supports multiple levels of parallelism.
In particular, it groups threads into \emph{teams}.
A \emph{thread team} is a collection of one or more parallel ``threads'' of execution.
Kokkos allows an arbitrary number of teams -- the \emph{league size}.
Hardware constrains the number of threads in a team -- the \emph{team size}.

Threads in a team can synchronize -- they have a ``barrier'' primitive -- 
and share a ``scratch pad'' memory which they may use for temporary storage.
Scratch pad memory exists only during parallel operations;
allocations in it do not persist across kernels.
Teams themselves may run in any order,
and may not necessarily run all in parallel.
For example, if the user asks for $T$ teams,
the hardware may choose to run them one after another in sequence,
or in groups of up to $G$ teams at a time in parallel.

Users may \emph{nest} parallel operations.
Teams may perform one parallel operation (for, reduce, or scan),
and threads within each team may perform another, possibly different parallel operation.
Different teams may do entirely different things.
For example, all the threads in one team may execute a \lstinline!parallel_for!,
and all the threads in a different team may execute a \lstinline!parallel_scan!.
Different threads within a team may also do different things.
However, performance may vary if threads in a team ``diverge'' in their behavior
(e.g., take different sides of a branch).
Chapter \ref{C:Hierarchical} shows how the C++ implementation of Kokkos exposes thread teams.

NVIDIA's CUDA programming model inspired Kokkos' thread team model.
The scratch pad memory corresponds with CUDA's per-team ``shared memory.''
The ``league / team'' vocabulary comes from OpenMP 4.0,
and has many aspects in common with our thread team model.
We have found that programming to this model results in good performance,
even on computer architectures which only implement parts of the full model.
For example, most multicore processors in common use for high-performance computing lack ``scratch pad'' hardware.
However, if users request a scratch pad size that fits comfortably in the largest cache shared by the threads in a team,
programming as if a scratch pad exists forces users to address locality in their algorithms.
This also reflects the common experience that rewriting a code for more restrictive hardware,
then porting the code \emph{back} to conventional hardware,
tends to improve performance relative to an unoptimized code.

>>>>

\section{Kokkos Execution Spaces}

@@

\subsection{Execution Space Instances}

@@

\subsection{Instances of Kokkos Memory Spaces}

@@

%\section{Thread teams}\label{S:Model:Teams}
%
%Kokkos supports multiple levels of parallelism.
%In particular, it groups threads into \emph{teams}.
%A \emph{thread team} is a collection of one or more parallel ``threads'' of execution.
%Kokkos allows an arbitrary number of teams -- the \emph{league size}.
%Hardware constrains the number of threads in a team -- the \emph{team size}.
%
%Threads in a team can synchronize -- they have a ``barrier'' primitive -- 
%and share a ``scratch pad'' memory which they may use for temporary storage.
%Scratch pad memory exists only during parallel operations;
%allocations in it do not persist across kernels.
%Teams themselves may run in any order,
%and may not necessarily run all in parallel.
%For example, if the user asks for $T$ teams,
%the hardware may choose to run them one after another in sequence,
%or in groups of up to $G$ teams at a time in parallel.
%
%Users may \emph{nest} parallel operations.
%Teams may perform one parallel operation (for, reduce, or scan),
%and threads within each team may perform another, possibly different parallel operation.
%Different teams may do entirely different things.
%For example, all the threads in one team may execute a \lstinline!parallel_for!,
%and all the threads in a different team may execute a \lstinline!parallel_scan!.
%Different threads within a team may also do different things.
%However, performance may vary if threads in a team ``diverge'' in their behavior
%(e.g., take different sides of a branch).
%Chapter \ref{C:Hierarchical} shows how the C++ implementation of Kokkos exposes thread teams.
%
%NVIDIA's CUDA programming model inspired Kokkos' thread team model.
%The scratch pad memory corresponds with CUDA's per-team ``shared memory.''
%The ``league / team'' vocabulary comes from OpenMP 4.0,
%and has many aspects in common with our thread team model.
%We have found that programming to this model results in good performance,
%even on computer architectures which only implement parts of the full model.
%For example, most multicore processors in common use for high-performance computing lack ``scratch pad'' hardware.
%However, if users request a scratch pad size that fits comfortably in the largest cache shared by the threads in a team,
%programming as if a scratch pad exists forces users to address locality in their algorithms.
%This also reflects the common experience that rewriting a code for more restrictive hardware,
%then porting the code \emph{back} to conventional hardware,
%tends to improve performance relative to an unoptimized code.

### 2015-04-15 Kokkos_PG_ParallelDispatch.tex
Convert to SAND format.
Updated style of the Guide . This comments out the SAND Report style
The stuff is still in if we really need to its not that hard to go back.

Kokkos lets users specify a scan by either a functor or a lambda.
Both look like their \lstinline!parallel_reduce! equivalents,
except that the \lstinline!operator()! method or lambda takes three arguments:
the loop index, the ``update'' value by nonconst reference, and a \lstinline!bool!.
Here is a lambda example where the intermediate results have type \lstinline!float!.
\begin{lstlisting}
View<float*> x = ...; // assume filled with input values
const size_t N = x.dimension_0 ();
parallel_scan (N, KOKKOS_LAMBDA (const int i, float& upd, const bool final) {
    if (final) {
      x(i) = upd; // only update array on final pass
    }
    // For exclusive scan, change the update value after 
    // updating array, like we do here.  For inclusive scan, 
    // change the update value before updating array.
    upd += x(i); 
  });
\end{lstlisting}
Kokkos may use a multiple-pass algorithm to implement scan.
This means that it may call your \lstinline!operator()! or lambda multiple times per loop index value.
The \lstinline!final! Boolean argument tells you whether Kokkos is on the final pass.
You must only update the array on the final pass.

@@

\section{Functors}
\section{Function Name Tags}

>>>>

Kokkos lets users specify a scan by either a functor or a lambda.
Both look like their \lstinline!parallel_reduce! equivalents,
except that the \lstinline!operator()! method or lambda takes three arguments:
the loop index, the ``update'' value by nonconst reference, and a \lstinline!bool!.
Here is a lambda example where the intermediate results have type \lstinline!float!.
\begin{lstlisting}
View<float*> x = ...; // assume filled with input values
const size_t N = x.dimension_0 ();
parallel_scan (N, KOKKOS_LAMBDA (const int& i, 
          float& upd, const bool& final) {
    if (final) {
      x(i) = upd; // only update array on final pass
    }
    // For exclusive scan, change the update value after 
    // updating array, like we do here.  For inclusive scan, 
    // change the update value before updating array.
    upd += x(i); 
  });
\end{lstlisting}
Kokkos may use a multiple-pass algorithm to implement scan.
This means that it may call your \lstinline!operator()! or lambda multiple times per loop index value.
The \lstinline!final! Boolean argument tells you whether Kokkos is on the final pass.
You must only update the array on the final pass.

@@

\section{Function Name Tags}

When writing class based applications it often is useful to make the classes themselves functors.
Using that approach allows the kernels to access all other class members, both data and functions. 
An issue coming up in that case is the necessity for multiple parallel kernels in the same class.
Kokkos supports that through function name tags. An application can use optional (unused) first arguments
to differentiate multiple operators in the same class. Execution policies can take the type of that argument as
an optional template parameter. The same applies to init, join and final functions.

\begin{lstlisting}
class Foo {
  struct BarTag {};
  struct RabTag {};

  void compute() {
     Kokkos::parallel_for(RangePolicy<BarTag>(0,100), *this);
     Kokkos::parallel_for(RangePolicy<RabTag>(0,1000), *this);
  }

  KOKKOS_INLINE_FUNCTION
  void operator() (const BarTag&, const int& i) const {
    ...
    foobar();
    ...
  }

  KOKKOS_INLINE_FUNCTION
  void operator() (const RabTag&, const int& i) const {
    ...
    foobar();
    ...
  }

  void foobar() {
    ...
  }
};
\end{lstlisting}

### 2015-04-15 Kokkos_PG_ProgrammingModel.tex
Convert to SAND format.
Updated style of the Guide . This comments out the SAND Report style
The stuff is still in if we really need to its not that hard to go back.

An Execution Space is the place {\it Where} code can actually be executed. 
For example on current Hybrid GPU / CPU systems there are two types of execution spaces: the GPU cores and the CPU cores. 
In the future this could include Processing in Memory (PIM) modules or different core types on a heterogenous CPU.
In principle this can also be used to introduce remote memory spaces, e.g. the capability of sending work to a different node.
Execution Spaces thus give an application developer the means to target different parts of a heterogenous hardware architecture.

@@

An Execution Policy determines together with an Execution Pattern {\it How} a function is executed.

>>>>

An Execution Space is the place {\it Where} code can actually be executed. 
For example on current Hybrid GPU / CPU systems there are two types of execution spaces: the GPU cores and the CPU cores. 
In the future this could include Processing in Memory (PIM) modules or different core types on a heterogenous CPU.
In principle this can also be used to introduce remote memory spaces, e.g. the capability of sending work to a different node.
Execution Spaces thus give an application developer the means to target different parts of a heterogenous hardware architecture.
This corresponds directly to the previously described machine model.

@@

An Execution Policy determines together with an Execution Pattern {\it How} a function is executed.
Some policies can be nested in others.

\subsection{Range Policies}

The most simple form of execution policies are {\it Range Policies}. 
They are used to execute an operation once for each element in a range. 
There are no prescriptions of order of execution or concurrency, which means that it is not legal
to synchronize different iterations.

\subsection{Team Policies}

Team policies are used to implement hierarchical parallelism. 
For that purpose Kokkos groups threads into \emph{teams}.
A \emph{thread team} is a collection of one or more parallel ``threads'' of execution.
Kokkos allows an arbitrary number of teams -- the \emph{league size}.
Hardware constrains the number of threads in a team -- the \emph{team size}.
All threads in a team are guaranteed to run concurrently.

Threads in a team can synchronize -- they have a ``barrier'' primitive -- 
and share a ``scratch pad'' memory which they may use for temporary storage.
Note that the not all forms of synchronization mechanism are legal in Kokkos, in particular
implementing ``spin-locks'' for threads in a team may result in dead locks. 
In Kokkos there is no forward progress guarantee for threads, that means that a single thread spinning
on a lock acquired by another thread of the team may use 100\% of the compute engines resources.
Calling the explicit Kokkos team barrier is the only safe way to synchronize threads in a team.

Scratch pad memory exists only during parallel operations;
allocations in it do not persist across kernels.
Teams themselves may run in any order,
and may not necessarily run all in parallel.
For example, if the user asks for $T$ teams,
the hardware may choose to run them one after another in sequence,
or in groups of up to $G$ teams at a time in parallel.

Users may \emph{nest} parallel operations.
Teams may perform one parallel operation (for, reduce, or scan),
and threads within each team may perform another, possibly different parallel operation.
Different teams may do entirely different things.
For example, all the threads in one team may execute a \lstinline!parallel_for!,
and all the threads in a different team may execute a \lstinline!parallel_scan!.
Different threads within a team may also do different things.
However, performance may vary if threads in a team ``diverge'' in their behavior
(e.g., take different sides of a branch).
Chapter \ref{C:Hierarchical} shows how the C++ implementation of Kokkos exposes thread teams.

NVIDIA's CUDA programming model inspired Kokkos' thread team model.
The scratch pad memory corresponds with CUDA's per-team ``shared memory.''
The ``league / team'' vocabulary comes from OpenMP 4.0,
and has many aspects in common with our thread team model.
We have found that programming to this model results in good performance,
even on computer architectures which only implement parts of the full model.
For example, most multicore processors in common use for high-performance computing lack ``scratch pad'' hardware.
However, if users request a scratch pad size that fits comfortably in the largest cache shared by the threads in a team,
programming as if a scratch pad exists forces users to address locality in their algorithms.
This also reflects the common experience that rewriting a code for more restrictive hardware,
then porting the code \emph{back} to conventional hardware,
tends to improve performance relative to an unoptimized code.

### 2015-04-15 Kokkos_PG_Views.tex
Updated style of the Guide . This comments out the SAND Report style
The stuff is still in if we really need to its not that hard to go back.

Kokkos selects a View's default layout for optimal parallel access
over the leftmost dimension, based on its execution space.  For
example, \lstinline!View<int**, Cuda>! has \lstinline!LayoutLeft!, so that
consecutive threads in the same warp access consecutive entries in
memory.  This \emph{coalesced access} gives the code better memory
bandwidth.  In contrast, \lstinline!View<int**, OpenMP>! has
\lstinline!LayoutRight!, so that a single thread accesses contiguous
entries of the array.  This avoids wasting cache lines and helps
prevent false sharing of a cache line between threads. 
In section \ref{S:View:Placement} more details will be discussed.

@@

\begin{lstlisting}
View<double*, MemoryTraits<SomeTrait> > a;
View<const double*, MemoryTraits<SomeTrait | SomeOtherTrait> > b;
View<double*, LayoutLeft, MemoryTraits<SomeTrait | SomeOtherTrait> > c;
View<double*, MemorySpace, MemoryTraits<SomeTrait | SomeOtherTrait> > d;
View<double*, LayoutLeft, MemorySpace, MemoryTraits<SomeTrait> > e;
\end{lstlisting}

>>>>

Kokkos selects a View's default layout for optimal parallel access
over the leftmost dimension, based on its execution space.  For
example, \lstinline!View<int**, Cuda>! has \lstinline!LayoutLeft!, so that
consecutive threads in the same warp access consecutive entries in
memory.  This \emph{coalesced access} gives the code better memory
bandwidth.

In contrast, \lstinline!View<int**, OpenMP>! has
\lstinline!LayoutRight!, so that a single thread accesses contiguous
entries of the array.  This avoids wasting cache lines and helps
prevent false sharing of a cache line between threads. 
In section \ref{S:View:Placement} more details will be discussed.

@@

\begin{lstlisting}
View<double*, MemoryTraits<SomeTrait> > a;
View<const double*, MemoryTraits<SomeTrait | SomeOtherTrait> > b;
View<int*, LayoutLeft, MemoryTraits<SomeTrait | SomeOtherTrait> > c;
View<int*, MemorySpace, MemoryTraits<SomeTrait | SomeOtherTrait> > d;
View<int*, LayoutLeft, MemorySpace, MemoryTraits<SomeTrait> > e;
\end{lstlisting}
